Summer 2025 ToDo

### 2025-07-25 Relations/Paper/WF_diagram.tex
wf diagram update

% Row 2: WFind
\node[box, below=of WFacc] (WFind) {WFind};
\node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
\node[box, right=of NNWFind] (WFindM) {WFind-};

\draw[arrow] (WFind) -- (NNWFind);
\draw[arrow] (NNWFind) -- (WFindM);

% Row 3: WFseq
\node[box, below=of WFind] (WFseq) {WFseq};
\node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=of NNWFseq] (WFseqM) {WFseq-};

@@

% Arrows between rows
\draw[arrow, <->] (WFacc) -- (WFind);
\draw[arrow, <->] (NNWFacc) -- (NNWFind);
\draw[arrow, <->] (WFaccM) -- (WFindM);

\draw[arrow] (WFind) to node[right, text = red] {Rdec} (WFseq);
\draw[arrow, bend left] (WFindM) to (WFseqM);
\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFindM);  
\draw[arrow, bend left = 45] (WFindM) to (WFminM);

@@

\draw[arrow, bend left=60] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);
\draw[arrow, bend right=45] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);

>>>>

% Row 2: WFind
% \node[box, below=of WFacc] (WFind) {WFind};
% \node[box, right=of WFind] (NNWFind) {$\lnot\lnot$WFind};
% \node[box, right=of NNWFind] (WFindM) {WFind-};

% \draw[arrow] (WFind) -- (NNWFind);
% \draw[arrow] (NNWFind) -- (WFindM);

% Row 3: WFseq
\node[box, below=of WFacc] (WFseq) {WFseq};
\node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=of NNWFseq] (WFseqM) {WFseq-};

@@

% Arrows between rows
% \draw[arrow, <->] (WFacc) -- (WFind);
% \draw[arrow, <->] (NNWFacc) -- (NNWFind);
% \draw[arrow, <->] (WFaccM) -- (WFindM);

\draw[arrow] (WFacc) to node[right, text = red] {Rdec} (WFseq);
\draw[arrow, bend left] (WFaccM) to (WFseqM);
\draw[arrow, bend left] (WFseqM) to node[left, text=red] {accCor} (WFaccM);  
\draw[arrow, bend left = 45] (WFaccM) to (WFminM);

@@

\draw[arrow, bend left=90] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend left=45] (WFminDNE) to node[pos=0.9, left, text=red] {Rdec$+$MP} (WFseq);
\draw[arrow, bend right=45] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
